Distinction Centrality Analysis

### 2025-07-18 analysis.qmd
new lays

```{r Toy Networks Plots}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1)
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2)
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3)
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4)
   dev.off()
   png(here("Plots", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "circle-plus-one.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
```

>>>>

```{r Toy Networks Plots}
   png(here("Plots", "star.png"))
   plot.graph.norm(g1, l = "auto")
   dev.off()
   png(here("Plots", "sf.png"))
   plot.graph.norm(g2, l = "auto")
   dev.off()
   png(here("Plots", "intra.png"))
   plot.graph.norm(g3, l = "auto")
   dev.off()
   png(here("Plots", "inter.png"))
   plot.graph.norm(g4, l = "auto")
   dev.off()
   png(here("Plots", "circle.png"))
   plot.graph.norm(g5, l = "circle")
   dev.off()
   png(here("Plots", "circle-plus-one.png"))
   plot.graph.norm(g6, l = "circle")
   dev.off()
```
